\documentclass[12pt]{article}

% ---------------- PACKAGES ----------------
\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{enumitem}

\setlength{\parskip}{0.5em}
\setlength{\parindent}{0pt}
\onehalfspacing

% ---------------- TITLE FORMAT ----------------
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

% ---------------- DOCUMENT ----------------
\begin{document}

\begin{center}
    \LARGE \textbf{Prototype Overview} \\
    \large Automated Solar Panel Dust Removal System \\
\end{center}

\vspace{0.5em}

% ------------------------------------------------
\section{Introduction}

This document presents a high-level overview of the Phase 3 prototype system developed to enable automated dust removal from solar panels using a non-abrasive film-based mechanism. The prototype integrates mechanical, structural, and control subsystems into a functional electromechanical system capable of periodic cleaning.

This overview summarizes the design, fabrication, integration, and verification processes undertaken, highlights key design decisions and implementation challenges, and evaluates the performance of the as-built system relative to the project specifications. It also serves as a roadmap to supporting artifacts contained within Sections 04.1–04.4 of the Design Dossier.

% ------------------------------------------------
\section{System Architecture}

The prototype system is composed of four primary subsystems:

\begin{itemize}
    \item \textbf{Mechanical Drive System:} GT2 timing belts driven by a single NEMA 17 stepper motor via a shared shaft
    \item \textbf{Film Transport System:} Transparent film attached to belts and translated across the panel surface
    \item \textbf{Structural Frame:} Laser-cut plywood structure supporting shafts, pulleys, and panel
    \item \textbf{Control System:} Raspberry Pi Pico W with A4988 driver executing timed actuation
\end{itemize}

\textbf{[INSERT FIGURE HERE: System Architecture Diagram]}  
\textit{Caption: System-level architecture of the as-built prototype showing subsystem interactions.}

% ------------------------------------------------
\section{From Concept to As-Built Prototype}

The Phase 2 concept proposed a belt-driven cleaning mechanism; however, several key implementation-level changes were required during Phase 3 to achieve a functional prototype:

\begin{itemize}
    \item Transition from multi-motor concepts to a \textbf{single stepper motor with shared shaft} to eliminate synchronization issues
    \item Replacement of conceptual materials with a \textbf{durable transparent film} sourced from MyFab
    \item Adoption of \textbf{stitched attachment} for reliability over repeated cycles
    \item Introduction of a \textbf{passive microfiber cleaning subsystem} to enable film reuse
    \item Simplification of control from wireless/sensor-based to a \textbf{standalone timed loop}
\end{itemize}

These modifications reflect a shift from conceptual feasibility to implementation-driven design.

\textbf{REFERENCE:} Prototype Design Converging Analysis (04.1) → \textit{INSERT LINK}

% ------------------------------------------------
\section{Detailed Prototype Design}

The as-built prototype consists of a $\sim$12$\times$12 inch laser-cut plywood frame supporting parallel GT2 timing belts looped over idler pulleys and a driven shaft. A transparent film is attached to the belts and spans across the solar panel surface.

A NEMA 17 stepper motor drives the system via a wooden dowel shaft coupled using a 3D-printed interface. The return path of the film passes over a microfiber cloth strip, which removes accumulated dust prior to re-entry.

The control system is implemented using a Raspberry Pi Pico W executing a timed actuation loop.

\textbf{[INSERT FIGURE HERE: Prototype Photograph]}  
\textit{Caption: As-built prototype system showing belt, film, and structural integration.}

\textbf{REFERENCES:}
\begin{itemize}
    \item Prototype Design Documentation (04.1) → \textit{INSERT LINK}
    \item Build Documentation (04.2) → \textit{INSERT LINK}
\end{itemize}

% ------------------------------------------------
\section{Iterative Design and Build Process}

The prototype was developed through iterative cycles of design, fabrication, and testing.

Initial iterations focused on validating belt tracking and film motion using temporary materials such as parchment paper and tape-based attachment. Subsequent iterations improved durability and alignment through material upgrades, stitched attachment, and structural refinements.

Key iterations included:
\begin{itemize}
    \item Belt tracking validation with temporary film
    \item Integration of full-width shaft for synchronized motion
    \item Transition to final film material and attachment method
    \item Addition of microfiber cleaning subsystem
\end{itemize}

\textbf{REFERENCES:}
\begin{itemize}
    \item Build Iterations (04.2) → \textit{INSERT LINK}
    \item Integration Process (04.3) → \textit{INSERT LINK}
\end{itemize}

% ------------------------------------------------
\section{Key Design Decisions}

Final design decisions were determined through trade-off analysis evaluating feasibility, reliability, and manufacturability:

\begin{itemize}
    \item \textbf{Single Motor Drive:} Eliminates synchronization risks between belts
    \item \textbf{Laser-Cut Plywood Frame:} Enables rapid iteration and easy modification
    \item \textbf{Wooden Dowel Shaft + Coupler:} Provides sufficient rigidity while remaining manufacturable
    \item \textbf{Stitched Film Attachment:} Improves durability over repeated cycles
    \item \textbf{Passive Microfiber Cleaning:} Enables film reuse with minimal added complexity
\end{itemize}

\textbf{REFERENCE:} Converging Trade-Off Analysis (04.1) → \textit{INSERT LINK}

% ------------------------------------------------
\section{Integration Challenges and Debugging}

Several key challenges were encountered during system integration:

\textbf{Belt-Pulley Height Mismatch:}  
Pulley flanges extended above the belt surface, preventing proper film contact. This was resolved by layering additional plastic material to elevate the contact surface.

\textbf{Shaft Friction:}  
Wood-on-wood contact between dowels and frame introduced excessive friction. This was mitigated by introducing a metal shaft coupler interface, reducing rotational resistance.

\textbf{Dowel Sizing and Alignment:}  
Material constraints required adaptation to available dowel sizes. Initial sanding solutions resulted in misalignment and uneven rotation. The final solution used smaller dowels with screw-based alignment.

\textbf{[INSERT FIGURES HERE: Debugging Images]}  
\textit{Caption: Examples of integration challenges and implemented fixes.}

\textbf{REFERENCE:} Integration Documentation (04.3) → \textit{INSERT LINK}

% ------------------------------------------------
\section{Prototype Performance Assessment}

The prototype successfully demonstrates:

\begin{itemize}
    \item Controlled advancement of film across the panel surface
    \item Reliable belt synchronization via single motor drive
    \item Feasibility of passive dust removal using microfiber cleaning
\end{itemize}

Limitations include:

\begin{itemize}
    \item Film tension and alignment require further refinement
    \item Long-term durability remains unverified
    \item Quantitative cleaning efficiency requires further testing
\end{itemize}

\textbf{REFERENCE:} Verification Results (04.4) → \textit{INSERT LINK}

% ------------------------------------------------
\section{Design Reflection and Concept Validation}

The prototype validates the feasibility of a belt-driven film cleaning mechanism and highlights synchronization, material durability, and simplicity of control as critical design considerations.

The system demonstrates that mechanical synchronization is essential for reliable operation, and that reducing system complexity improves robustness during early-stage prototyping.

These findings inform future iterations of the design concept.

% ------------------------------------------------
\section{Dossier Navigation}

This document serves as a roadmap to the Phase 3 work:

\begin{itemize}
    \item \textbf{04.1 Prototype Design:} Design decisions and trade-off analysis
    \item \textbf{04.2 Build:} Fabrication and iteration process
    \item \textbf{04.3 Integration:} Assembly challenges and debugging
    \item \textbf{04.4 Verification:} Testing and performance evaluation
\end{itemize}

\end{document}